Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-10 paper.tex
bugfix wrapfig and complete table
Minor formatting adjustments

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\usepackage{multirow}
\usepackage{tabularx}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

    \begin{tabularx}{\linewidth}{*{3}{>{\centering\arraybackslash}X}}
        Noisy Original & Clean Reproduction & Augraphy Reproduction \\
        \multicolumn{3}{c}{
            \resizebox{\textwidth}{!}{
                \includegraphics{figures/archetype-memo.pdf}}}      \\
        (a) & (b) & (c) \\
    \end{tabularx}

@@

\emph{Augraphy} has been used in several research efforts: Larson et al. (2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document deniosing GAN; and Kim et al. 2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{lccccc}
    \toprule
         & \textbf{Number of} & \textbf{Document} & \textbf{Pipeline} & & \\
        \textbf{Library} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\section{Document Distortion, Theory \& Technique}
Many approaches exist for adding features to an image, and many types of feature can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\

@@

A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers. These are cut to size and stacked, then bound in reams and sent out for sale and use. This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream. At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink. Any of these processes may alter the local texture or global topology of the sheet. The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations. Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\

Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle. Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.\\

Some techniques exist for introducing these features into images of documents, including but not limited to the following:
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
\end{enumerate}

Augraphy already has a story for the first three, with the fourth in planning.

@@

The value added by the \texttt{AugraphyPipeline} class over a bare list of functions applied in sequence to an image is principally in the collection of runtime metadata; the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation.
This allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure 1 \ref{fig:intro}.

\smallskip
There are also two classes that provide additional critical functionality in order to round out the \emph{Augraphy} base library:

@@

\smallskip
\noindent\textbf{\texttt{PaperFactory}.} ~We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.
We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline.
This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image.
The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database \cite{ref_NoisyOfficeDatabase}.
Taken together, \texttt{PaperFactory} makes it trivial to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{sectsty}
\usepackage{wrapfig}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

    \begin{tabularx}{\linewidth}{*{3}{>{\centering\arraybackslash}X}}
        Noisy Original & Clean Reproduction & Augraphy Reproduction \\
        \multicolumn{3}{c}{
            \resizebox{\textwidth}{!}{
                \includegraphics{figures/archetype-memo.pdf}}}      \\
        %(a) & (b) & (c) \\
    \end{tabularx}

@@

\emph{Augraphy} has been used in several research efforts: Larson et al. (2022) \cite{larson-2022-rvlcdip-ood} used \emph{Augraphy} to mimic scanner-like noise for evaluating document classifiers trained on RVL-CDIP; Jadhav et al 2022 \cite{jadhav2022pix2pix} used \emph{Augraphy} to generate noisy document images for training a document denoising GAN; and Kim et al. 2022 \cite{webvicob-2022-naver} used \emph{Augraphy} as part of a document generation pipeline for document understanding tasks.

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{lccccc}
    \toprule
         & \textbf{Number of} & \textbf{Document} & \textbf{Pipeline} & & \\
        \textbf{Library} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark & \cmark  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & \cmark & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\section{Document Distortion, Theory \& Technique}
Many approaches exist for adding features to an image, and many types of features can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.

@@

A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers. These are cut to size and stacked, then bound in reams and sent out for sale and use. This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream. At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink. Any of these processes may alter the local texture or global topology of the sheet. The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations. Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.

Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle. Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.

Some techniques exist for introducing these features into images of documents, including but not limited to the following:
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator's 3D mesh support here is excellent and has inspired Augraphy to add similar functionality in its roadmap.  In the meantime, Augraphy currently offers support for paper folds.
\end{enumerate}

@@

The value added by the \texttt{AugraphyPipeline} class over a bare list of functions applied in sequence to an image is principally in the collection of runtime metadata; the output of an \texttt{AugraphyPipeline} application is a Python dictionary which contains not only the final image, but copies of every intermediate image, as well as information about the object constructors and their parameters that were used for each augmentation. 
 This pipeline metadata allows for easy inspection and fine-tuning of the pipeline definition to achieve outputs with desired features, facilitating (re)production of documents as in Figure \ref{fig:intro}.

\sectionfont{\keepall}
There are also two classes that provide additional critical functionality in order to round out the \emph{Augraphy} base library:

@@

\sectionfont{\normalfont}
\noindent\textbf{\texttt{PaperFactory}.} ~We often print on multiple sizes and kinds of paper, and out in the world we certainly \textit{encounter} such diverse documents.
We introduce this variation into the \texttt{AugmentationPipeline} by including \texttt{PaperFactory} in the \texttt{paper} phase of the pipeline.
This augmentation checks a local directory for images of paper to crop, scale, and use as a background for the document image.
The pipeline contains edge detection logic for lifting only text and other foreground objects from a clean image, greatly simplifying the ``printing" onto another ``sheet", and capturing in a reproducible way the construction method used to generate the NoisyOffice database \cite{ref_NoisyOfficeDatabase}.
Taken together, \texttt{PaperFactory} makes it trivial to re-print a document onto other surfaces, like hemp paper, cardboard, or wood.
